---
title: "Multivariate analysis of genetic data: an introduction -- with Grant's Gazelle SNP Data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Install the stable version of adegenet with dependencies

```{r}
install.packages("adegenet", dep=TRUE)
install.packages("hierfstat", dep=TRUE)
```

Load the useful packages

```{r, echo=FALSE}
library("adegenet")
library("hierfstat")
```

```

Load STRUCTURE .stru file

```{r}
data_local_stru <- read.structure("../grants_package/processed/structure/locality_grants.stru", n.ind=95, n.loc=7566, onerowperind=FALSE, col.lab=1, col.pop=2, row.marknames=1, ask=FALSE)
popNames(data_local_stru)<-c("Amboseli", "Mkomazi_E", "Burigi", "Ikiri-Rungwa", "Aruba_Dam", "Ugalla", "Masai_Mara",	"Nairobi",	"Samburu",	"Tsavo",	"Sibiloi",	"Monduli", "Maswa","Mkomazi_W")
```


## pairwise Fst
```{r}
dist_WC84 <- genet.dist(data_local_stru, method = "WC84")
```


```{r}
pw_WCfst <- pairwise.WCfst(genind2hierfstat(data_local_stru))
pw_fst_CI <- boot.ppfst(genind2hierfstat(data_local_stru),nboot=100,quant=c(0.025,0.975),diploid=TRUE,dig=4)
```



## pairwise genetic distance

```{r}
pop_local_stru <- genind2genpop(data_local_stru)

pw_dist_stru <- dist.genpop(pop_local_stru, method = 1, diag = TRUE, upper = TRUE)
```
